Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-06 ms/ms.Rmd
ms: remove template appendices

---
title: Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'soil')`"
author:
  - given_name: Julien
    surname: Vollering
    affiliation: 1
    email: julien.vollering@hvl.no
    corresponding: true
  - given_name: Naomi
    surname: Gatis
    affiliation: 2
  - given_name: Mette
    surname: Kusk Gillespie
    affiliation: 1
  - given_name: Karl-Kristian
    surname: Muggerud
    affiliation: 1
  - given_name: Sigurd Daniel
    surname: Nerhus
    affiliation: 1
  - given_name: Knut
    surname: Rydgren
    affiliation: 1
  - given_name: Mikko
    surname: Sparf
    affiliation: 1
affiliation:
  - code: 1
    address: Department of Civil Engineering and Environmental Sciences, Western Norway University of Applied Sciences, Norway
  - code: 2
    address: Department of Geography, University of Exeter, United Kingdom
abstract: |
  The abstract goes here.
  It can also be on _multiple lines_.
bibliography: ms.bib
running:
  title: Peat depth from terrain and radiometrics
  author: Vollering et al.
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: |
  *Competing interests.* The authors declare that they have no conflict of interest.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #code: |
  #  use this to add a statement when having only software code available
  #data: |
  #  use this to add a statement when having only data sets available
  codedata: |
    *Code and data availability.* Use this to add a statement when having data sets and software code available
authorcontribution: |
  *Author contributions.*
  JV: Conceptualization, Investigation, Data curation, Formal analysis, Writing – original draft.
  NG: Conceptualization, Methodology, Writing - review & editing.
  MKG: Investigation, Writing - review & editing.
  KKM: Investigation, Data curation, Writing - review & editing.
  SDN: Investigation, Writing - review & editing.
  KR: Conceptualization, Investigation, Writing - review & editing.
  MS: Investigation, Data curation, Writing - review & editing.
disclaimer: |
  *Disclaimer.* The authors declare that the results, discussions, and interpretations presented in this study are solely their own. The views expressed herein do not necessarily reflect those of their respective institutions or funding agencies.
acknowledgements: |
  *Acknowledgements.* We thank the Norwegian Public Roads Administration for sharing data from ground-penetrating radar surveys. We also thank Vikas Baranwal from the Geological Survey of Norway for helping us access the radiometric data from Skrim. This work contains data under the following licenses: (1) Creative Commons Attribution 4.0 International, © Kartverket, (2) *Norge digitalt* license, Norwegian Institute of Bioeconomy Research (NIBIO), © Geovekst, and (3) the Norwegian License for Public Data (NLOD), made available by the Geological Survey of Norway (NGU).
appendix: |
  \section{For submission}
  "Appendices: all material required to understand the essential aspects of the paper
  such as experimental methods, data, and interpretation 
  should preferably be included in the main text. 
  Additional figures, tables, as well as technical and theoretical developments 
  which are not critical to support the conclusion of the paper,
  but which provide extra detail and/or support useful for experts in the field
  and whose inclusion in the main text would disrupt the flow of descriptions or demonstrations 
  may be presented as appendices.
  These should be labelled with capital letters: Appendix A, Appendix B etc.
  Equations, figures and tables should be numbered as (A1), Fig. B5 or Table C6, respectively.
  Please keep in mind that appendices are part of the manuscript
  whereas supplements (see below) are published along with the manuscript."

  \section{Figures and tables in appendices}
  Please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.

  \section{Copernicus from Rmarkdown}
  **Please note:** Per [their guidelines](https://publications.copernicus.org/for_authors/manuscript_preparation.html),
  Copernicus does not support additional \LaTeX{} packages 
  or new \LaTeX{} commands than those defined in their `.cls` file. 
  This means that you cannot add any extra dependencies 
  and a warning will be thrown if so.
  **Important**: Always double-check with the official manuscript preparation guidelines 
  at [https://publications.copernicus.org/for_authors/manuscript_preparation.html](https://publications.copernicus.org/for_authors/manuscript_preparation.html),
  especially the sections "Technical instructions for LaTeX" and "Manuscript composition". 
  Please contact Daniel Nüst, `daniel.nuest@uni-muenster.de`, with any problems.
output:
  bookdown::pdf_book:
    keep_md: true
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

>>>>

---
title: Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'soil')`"
author:
  - given_name: Julien
    surname: Vollering
    affiliation: 1
    email: julien.vollering@hvl.no
    corresponding: true
  - given_name: Naomi
    surname: Gatis
    affiliation: 2
  - given_name: Mette
    surname: Kusk Gillespie
    affiliation: 1
  - given_name: Karl-Kristian
    surname: Muggerud
    affiliation: 1
  - given_name: Sigurd Daniel
    surname: Nerhus
    affiliation: 1
  - given_name: Knut
    surname: Rydgren
    affiliation: 1
  - given_name: Mikko
    surname: Sparf
    affiliation: 1
affiliation:
  - code: 1
    address: Department of Civil Engineering and Environmental Sciences, Western Norway University of Applied Sciences, Norway
  - code: 2
    address: Department of Geography, University of Exeter, United Kingdom
abstract: |
  The abstract goes here.
  It can also be on _multiple lines_.
bibliography: ms.bib
running:
  title: Peat depth from terrain and radiometrics
  author: Vollering et al.
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: |
  *Competing interests.* The authors declare that they have no conflict of interest.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #code: |
  #  use this to add a statement when having only software code available
  #data: |
  #  use this to add a statement when having only data sets available
  codedata: |
    *Code and data availability.* Use this to add a statement when having data sets and software code available
authorcontribution: |
  *Author contributions.*
  JV: Conceptualization, Investigation, Data curation, Formal analysis, Writing – original draft.
  NG: Conceptualization, Methodology, Writing - review & editing.
  MKG: Investigation, Writing - review & editing.
  KKM: Investigation, Data curation, Writing - review & editing.
  SDN: Investigation, Writing - review & editing.
  KR: Conceptualization, Investigation, Writing - review & editing.
  MS: Investigation, Data curation, Writing - review & editing.
disclaimer: |
  *Disclaimer.* The authors declare that the results, discussions, and interpretations presented in this study are solely their own. The views expressed herein do not necessarily reflect those of their respective institutions or funding agencies.
acknowledgements: |
  *Acknowledgements.* We thank the Norwegian Public Roads Administration for sharing data from ground-penetrating radar surveys. We also thank Vikas Baranwal from the Geological Survey of Norway for helping us access the radiometric data from Skrim. This work contains data under the following licenses: (1) Creative Commons Attribution 4.0 International, © Kartverket, (2) *Norge digitalt* license, Norwegian Institute of Bioeconomy Research (NIBIO), © Geovekst, and (3) the Norwegian License for Public Data (NLOD), made available by the Geological Survey of Norway (NGU).
output:
  bookdown::pdf_book:
    keep_md: true
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

### 2024-11-06 ms/ms.tex
ms: remove template appendices

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{For submission}

``Appendices: all material required to understand the essential aspects of the paper
such as experimental methods, data, and interpretation
should preferably be included in the main text.
Additional figures, tables, as well as technical and theoretical developments
which are not critical to support the conclusion of the paper,
but which provide extra detail and/or support useful for experts in the field
and whose inclusion in the main text would disrupt the flow of descriptions or demonstrations
may be presented as appendices.
These should be labelled with capital letters: Appendix A, Appendix B etc.
Equations, figures and tables should be numbered as (A1), Fig. B5 or Table C6, respectively.
Please keep in mind that appendices are part of the manuscript
whereas supplements (see below) are published along with the manuscript.''

\section{Figures and tables in appendices}

Please also sort the appendix figures and appendix tables into the respective appendix sections.
They will be correctly named automatically.

\section{Copernicus from Rmarkdown}

\textbf{Please note:} Per \href{https://publications.copernicus.org/for_authors/manuscript_preparation.html}{their guidelines},
Copernicus does not support additional \LaTeX{} packages
or new \LaTeX{} commands than those defined in their \texttt{.cls} file.
This means that you cannot add any extra dependencies
and a warning will be thrown if so.
\textbf{Important}: Always double-check with the official manuscript preparation guidelines
at \url{https://publications.copernicus.org/for_authors/manuscript_preparation.html},
especially the sections ``Technical instructions for LaTeX'' and ``Manuscript composition''.
Please contact Daniel Nüst, \texttt{daniel.nuest@uni-muenster.de}, with any problems.
\noappendix

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
